Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-27 Docs/IJES/journal.tex
improving comment A-16

Algorithm in Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed. 
Note that the algorithm is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
From lines $4$ to $9$, the algorithm finds the largest interval. Then, from line $10$ the largest interval is removed and the median is calculated in line $11$. After that, two new intervals are created, the left-side (in line $14$) and the right-side (in line $18$). At the end, the median is returned.

@@

Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.

>>>>

Algorithm in Figure~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed. 
Note that the algorithm is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned. \textcolor{blue}{Furthermore, this algorithm is synchronized, which ensures a unique step value for a worker request.}
From lines $4$ to $9$, the algorithm finds the largest interval. Then, from line $10$ the largest interval is removed and the median is calculated in line $11$. After that, two new intervals are created, the left-side (in line $14$) and the right-side (in line $18$). At the end, the median is returned.

@@

Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$); otherwise, the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.  \textcolor{blue}{It is worth mentioning that there is no interchange communication among the workers, but they are responsible to notify the controller if a violation is found.}
